exploratory

### 2021-11-13 code/analysis_code/analysisscript.Rmd
Further Analysis completed

# saved it as a file
```{r}
summarytable_file12 = here("results", "lg_fit_table_predisposing.rds")
saveRDS(lg_fit_table_predisposing, file = summarytable_file12)
```

@@

# saved it as a file
```{r}
summarytable_file13 = here("results", "lg_fit_statistics_predisposing.rds")
saveRDS(lg_fit_statistics_predisposing, file = summarytable_file13)
```

@@

# saved it as a file
```{r}
summarytable_file14 = here("results", "lg_fit_table_enabling.rds")
saveRDS(lg_fit_table_enabling, file = summarytable_file14)
```

@@

# saved it as a file
```{r}
summarytable_file15 = here("results", "lg_fit_statistics_enabling.rds")
saveRDS(lg_fit_statistics_enabling, file = summarytable_file15)
```

@@

# saved it as a file
```{r}
summarytable_file16 = here("results", "lg_fit_table_needforcare.rds")
saveRDS(lg_fit_table_needforcare, file = summarytable_file16)
```

@@

# saved it as a file
```{r}
summarytable_file17 = here("results", "lg_fit_statistics_needforcare.rds")
saveRDS(lg_fit_statistics_needforcare, file = summarytable_file17)
```

@@

#make a model
#choose multinom_reg() + nnet
```{r}
mydata_model <- 
  multinom_reg() %>% 
  set_engine("nnet")
```

@@

# Put 70% of the data into the training set and 30% into testing using strata=BodyTemp
```{r}
data_split <- initial_split(mydata, prop = 0.7, strata = infection_status_info)
```

# Create data frames for the two sets:
```{r}
train_data <- training(data_split)
test_data  <- testing(data_split)
```

# training set proportions by class
```{r}
train_data %>% 
  count(infection_status_info) %>% 
  mutate(prop = n/sum(n))
```

# test set proportions by class
```{r}
test_data %>% 
  count(infection_status_info) %>% 
  mutate(prop = n/sum(n))
```
##5-fold cross validation, 5 times repeated, stratified on `infection status` for the CV folds
```{r}
mydata_folds <- vfold_cv(train_data, v = 5, repeats =5, strata= "infection_status_info")
```

@@

#fit
```{r}
mydata_fit <- 
 mydata_wf %>% 
  fit_resamples(mydata_folds)
```

#metrics
```{r}
collect_metrics(mydata_fit)
```

>>>>

#saved it as a file
```{r}
summarytable_file12 = here("results", "lg_fit_table_predisposing.rds")
saveRDS(lg_fit_table_predisposing, file = summarytable_file12)
```

@@

#saved it as a file
```{r}
summarytable_file13 = here("results", "lg_fit_statistics_predisposing.rds")
saveRDS(lg_fit_statistics_predisposing, file = summarytable_file13)
```

@@

#saved it as a file
```{r}
summarytable_file14 = here("results", "lg_fit_table_enabling.rds")
saveRDS(lg_fit_table_enabling, file = summarytable_file14)
```

@@

#saved it as a file
```{r}
summarytable_file15 = here("results", "lg_fit_statistics_enabling.rds")
saveRDS(lg_fit_statistics_enabling, file = summarytable_file15)
```

@@

#saved it as a file
```{r}
summarytable_file16 = here("results", "lg_fit_table_needforcare.rds")
saveRDS(lg_fit_table_needforcare, file = summarytable_file16)
```

@@

#saved it as a file
```{r}
summarytable_file17 = here("results", "lg_fit_statistics_needforcare.rds")
saveRDS(lg_fit_statistics_needforcare, file = summarytable_file17)
```

@@

#**Analysis for Part 4 starts here**  
#make a model
#choose multinom_reg() + nnet
```{r}
mydata_model <- 
  multinom_reg() %>% 
  set_engine("nnet")
```

@@

#Put 70% of the data into the training set and 30% into testing using strata=BodyTemp
```{r}
data_split <- initial_split(mydata, prop = 0.7, strata = infection_status_info)
```

#Create data frames for the two sets:
```{r}
train_data <- training(data_split)
test_data  <- testing(data_split)
```

#training set proportions by class
```{r}
train_data %>% 
  count(infection_status_info) %>% 
  mutate(prop = n/sum(n))
```

#test set proportions by class
```{r}
test_data %>% 
  count(infection_status_info) %>% 
  mutate(prop = n/sum(n))
```
##5-fold cross validation, 5 times repeated, stratified on `infection status` for the CV folds with training data
```{r}
mydata_folds <- vfold_cv(train_data, v = 5, repeats =5, strata= "infection_status_info")
```

@@

#fitting the training data
```{r}
training_data_fit <- 
 mydata_wf %>% 
  fit_resamples(mydata_folds)
```

#metrics of training data
```{r}
collect_metrics(training_data_fit)
```
##5-fold cross validation, 5 times repeated, stratified on `infection status` for the CV folds with test data
```{r}
mydata_folds2 <- vfold_cv(test_data, v = 5, repeats =5, strata= "infection_status_info")
```
#fitting the test data
```{r}
test_data_fit <- 
 mydata_wf %>% 
  fit_resamples(mydata_folds2)
```

#metrics of test data
```{r}
collect_metrics(test_data_fit)
```

### 2021-11-13 code/analysis_code/exploratory.Rmd
Further Analysis completed

```{r}
data1 %>% 
     group_by( `student/heathworker` ) %>% 
     summarise( percent = 100 * n() / nrow( data1) )
```

@@

```{r}
table(data1$`Do you have any of the following chronic/underlying diseases? (many answers possible): Heart disease`)
```
```{r}
table(data1$`Do you have any of the following chronic/underlying diseases? (many answers possible): Hypertension`)
```
```{r}
table(data1$`Do you have any of the following chronic/underlying diseases? (many answers possible): Diabetes`)
```
```{r}
table(data1$`Do you have any of the following chronic/underlying diseases? (many answers possible): Cancer`)
```
```{r}
table(data1$`Do you have any of the following chronic/underlying diseases? (many answers possible): HIV`)
```
```{r}
table(data1$`Do you have any of the following chronic/underlying diseases? (many answers possible): Tuberculosis`)
```
```{r}
table(data1$`Do you have any of the following chronic/underlying diseases? (many answers possible): Asthma`)
```
```{r}
table(data1$`Do you have any of the following chronic/underlying diseases? (many answers possible): None of the above`)
```
```{r}
chronic_disease_history = data1 %>% 
     group_by( `Do you have any of the following chronic/underlying diseases? (many answers possible): None of the above` ) %>% 
     summarise( percent = 100 * n() / nrow( data1) )
print(chronic_disease_history)
```

@@

#the next code basically summarizes the answers for each question:
```{r}
table(data1$`During the past 7 days, have you been observing any of the following preventive measures against COVID-19? (Tick all answers that apply): Social distancing of at least 1.5m`)
```
```{r}
table(data1$`During the past 7 days, have you been observing any of the following preventive measures against COVID-19? (Tick all answers that apply): Wearing face mask`)
```
```{r}
table(data1$`During the past 7 days, have you been observing any of the following preventive measures against COVID-19? (Tick all answers that apply): Hand hygiene (regular handwashing with soap or using hand gel)`)
```
```{r}
table(data1$`During the past 7 days, have you been observing any of the following preventive measures against COVID-19? (Tick all answers that apply): Coughing hygiene (covering mouth when coughing or sneezing)`)
```
```{r}
table(data1$`During the past 7 days, have you been observing any of the following preventive measures against COVID-19? (Tick all answers that apply): None of the above`)
```
```{r}
data1 %>% 
     group_by( `During the past 7 days, have you been observing any of the following preventive measures against COVID-19? (Tick all answers that apply): None of the above` ) %>% 
     summarise( percent = 100 * n() / nrow( data1) )
```

>>>>

```{r}
data1 %>% 
     group_by( `student_or_heathworker` ) %>% 
     summarise( percent = 100 * n() / nrow( data1) )
```

@@

```{r}
table(data1$`Do you have any of the following chronic/underlying diseases? (many answers possible): Heart disease`)
```
```{r}
table(data1$`Do you have any of the following chronic/underlying diseases? (many answers possible): Hypertension`)
```
```{r}
table(data1$`Do you have any of the following chronic/underlying diseases? (many answers possible): Diabetes`)
```
```{r}
table(data1$`Do you have any of the following chronic/underlying diseases? (many answers possible): Cancer`)
```
```{r}
table(data1$`Do you have any of the following chronic/underlying diseases? (many answers possible): HIV`)
```
```{r}
table(data1$`Do you have any of the following chronic/underlying diseases? (many answers possible): Tuberculosis`)
```
```{r}
table(data1$`Do you have any of the following chronic/underlying diseases? (many answers possible): Asthma`)
```
```{r}
table(data1$`Do you have any of the following chronic/underlying diseases? (many answers possible): None of the above`)
```
```{r}
chronic_disease_history = data1 %>% 
     group_by( `chronic_disease_history` ) %>% 
     summarise( percent = 100 * n() / nrow( data1) )
print(chronic_disease_history)
```

@@

#the next code basically summarizes the answers for each question:
```{r}
table(data1$`social_distance_practice`)
```
```{r}
table(data1$`During the past 7 days, have you been observing any of the following preventive measures against COVID-19? (Tick all answers that apply): Wearing face mask`)
```
```{r}
table(data1$`During the past 7 days, have you been observing any of the following preventive measures against COVID-19? (Tick all answers that apply): Hand hygiene (regular handwashing with soap or using hand gel)`)
```
```{r}
table(data1$`During the past 7 days, have you been observing any of the following preventive measures against COVID-19? (Tick all answers that apply): Coughing hygiene (covering mouth when coughing or sneezing)`)
```
```{r}
table(data1$`During the past 7 days, have you been observing any of the following preventive measures against COVID-19? (Tick all answers that apply): None of the above`)
```
```{r}
data1 %>% 
     group_by( `follow_preventive_measure` ) %>% 
     summarise( percent = 100 * n() / nrow( data1) )
```
